---
output: html_document
---

```{r setup}
library(knitr)
opts_chunk$set(message = FALSE, warning = FALSE)
```

# Smart and Interactive Documents

## Seeing is Believing

```{r}
counts <- c(4, 5, 6)
mean(counts)
```

Text and ...

Bulleted Lists

- SQL
- ...

Numbered Lists

6. SQL
1. ...

Tables

id | ...
...
1  | control
2  | exclosure

# The Biggest Heading

## ...

... The Third Biggest Heading

Chunks

```
The ... indicated by asterisks here does not become
italicized, as it would outside the "code fence".
```

```
seq(...)
```

## RMarkdown

```...
seq(1, 10)
```


...
seq(1, 10)
```


```{...}
seq(1, 10)
```


```{... load_data, echo = FALSE}
...
```


```{... bar_plot}
library(ggplot2)
ggplot(..., aes(x = species_id, y = count)) +
  geom_bar(stat = 'identity')
```


```{...}
greeting = 'Hello, {}!'
print(greeting.format('World'))
```


```{...}
echo "Hello, ${USER}!"
```


```{... clean_bar_plot, ...}
ggplot(rodents, aes(x = species_id, y = weight)) +
  geom_bar(stat = 'identity')
```


```{..., echo = FALSE}
...('pick_species',
  label = 'Pick a Species',
  choices = unique(species[['id']]))
```


```{..., context = 'server'}
library(dplyr)

... <- ...({
  animals %>%
    filter(species_id == input[['pick_species']]) %>%
    ggplot(aes(year)) + 
      geom_bar()
})
```


```{..., echo = FALSE}
...
```


```{..., context = 'server'}
plot_data <- ...
  filter(animals,
         species_id == input[['pick_species']])
})
output[['react_ts_plot']] <- renderPlot({
  ... %>%
    ggplot(aes(year)) +
      geom_bar()
})
```


```{..., echo = FASE}
plotOutput(...)
```
